---
title: "LER Analysis"
editor: visual
format: 
  html: 
    embed-resources: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(here)
# Bring in the function
source(here("ler_intercrop_function.R"))
```

## Introduction

The Land Equivalent Ratio (LER) is a key metric in intercropping to compare the efficiency of land use relative to monocropping. This analysis demonstrates the function using sample data.

## Sample Data

```{r generate-data}
# For reproducibility
set.seed(123) 

# Random yield for crop A (intercrop)
yield_intercrop_A <- runif(1, 2, 5)  

# Random yield for crop A (monocrop)
yield_mono_A <- runif(1, 4, 7)

# Random yield for crop B (intercrop)
yield_intercrop_B <- runif(1, 1, 3) 

# Random yield for crop B (monocrop)
yield_mono_B <- runif(1, 3, 6)       #

data.frame(yield_intercrop_A, yield_mono_A, yield_intercrop_B, yield_mono_B)
```

## Calculating LER

```{r calculate-ler}
LER_value <- calculate_LER(yield_intercrop_A, yield_mono_A, yield_intercrop_B, yield_mono_B)
LER_value
```

## Visualization

```{r plot-ler}
library(ggplot2)

data <- data.frame(
  Crop = c("Crop A", "Crop B"),
  Intercrop = c(yield_intercrop_A, yield_intercrop_B),
  Monocrop = c(yield_mono_A, yield_mono_B)
)

data_long <- reshape2::melt(data, id.vars = "Crop")

ggplot(data_long, aes(x = Crop, y = value, fill = variable)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = c("Intercrop" = "#1b9e77", "Monocrop" = "#d95f02")) +
  labs(title = "Intercropping vs. Monocropping Yields", y = "Yield", x = "Crop", fill = "System") +
  theme_classic()
```

#Reviewed this quarter file

## Conclusion

The LER calculation provides insight into the efficiency of intercropping versus monocropping. If LER \> 1, intercropping is beneficial; otherwise, monocropping may be preferable.
